Cooling Requirements for the Vertical Shear Instability in Protoplanetary Disks

### 2015-04-24 paper.tex
exceedingly minor end of workday commit.

\section{Thermodynamic requirement for the vertical shear instability}\label{vsi_require}     In this paper we will find that in a stably stratified thin disk, the VSI  
requires a thermal timescale $t_c$ much less than the
disk dynamical timescale, 
\begin{align}
  t _c \ll \OmK^{-1}. 
\end{align}
where $\OmK$ is the Keplerian frequency. 
To see why this should be expected, we need to compare vertical shear
with vertical buoyancy. For this preliminary discussion we consider a
vertically isothermal disk with aspect-ratio $ h$,  
dimensionless radial temperature gradient $q$ and adiabatic index
$\gamma$. For a PPD, $ h \sim 0.05$, $|q|\sim 1$ and $\gamma\simeq 1.4$.

>>>>

\section{Thermodynamic requirement for the vertical shear instability}\label{vsi_require}     In this paper we will find that in a stably stratified thin disk, the VSI  
requires a thermal timescale $t_c$ much shorter than the
disk dynamical timescale, 
\begin{align}
  t _c \ll \OmK^{-1}. 
\end{align}
where $\OmK$ is the Keplerian frequency, consistent with N13. 
To see why this should be expected, we need to compare vertical shear
with vertical buoyancy. For this preliminary discussion we consider a
vertically isothermal disk with aspect-ratio $ h$,  
dimensionless radial temperature gradient $q$ and adiabatic index
$\gamma$. For a PPD, $ h \sim 0.05$, $|q|\sim 1$ and $\gamma\simeq 1.4$.
